Universal Anonymous Signatures

### 2022-05-02 prism-backend/research/gsac/app-building-blocks.tex
Proofs for GSAC done (except correctnes...)

A digital signature scheme is correct if honestly generated signatures, using
honestly generated key pairs, are always accepted by \SVerify. \todo{define more
  formally?}
%
A digital signature scheme \S has existential unforgeability if, for all p.p.t.
adversaries $\adv$, $\Pr[\ExpEUF = 1]$ is a negligible function of the
security parameter.

\begin{figure}[ht!]
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpEUF(\Ssecpar)$}{%
      \Sparm \gets \SSetup(\Ssecpar) \\
      (\Svk,\Ssk) \gets \SKeyGen(\Sparm) \\
      (\Ssig,\msg) \gets \adv^{\SSign(\Ssk,\cdot)}(\Svk) \\
      \pcif \SVerify(\Svk,\Ssig,\msg) = 0: \pcreturn 0 \\
      \pcif \msg~\textrm{was not queried to \SSign}: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:euf-game}
  \caption{Existential Unforgeability Game.}
\end{figure}

@@

Defined as a tuple $(\ESetup,\EKeyGen,\EEnc,\EDec)$. Algorithm $\Eparm \gets
\ESetup(\Esecpar)$ produces public parameters for the other algorithms.
$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$ generates the encryption-decryption key
pair, algorithm $\Ec \gets \EEnc(\Eek,\msg)$ encrypts message \msg with
encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\Edk,
\Ec)$ decrypts ciphertexts using decryption key \Edk. \todo{Informally define
  security properties we'll need.}

@@

\begin{description}
\item[Binding.] Intuitively, the binding property of commitment schemes means
  that no adversary can change the message that has been committed to. More
  formally, $\Pr[\ExpComBind = 1]$ must be a negligible function of the security
  parameter.
\item[Hiding.] The hiding property captures that no adversary should be able to
  learn the message that was committed, when given only the commitment. This is
  formally defined through \ExpComHideb, where $|\Pr[\ExpComHideb=1|b=1] -
  \Pr[\ExpComHideb=1|b=0]|$ must be a negligible function of the security
  parameter.
\end{description}

\todo{Commitments with proofs, needed for \SBCM.}

\begin{figure}[ht!]
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpComBind(\secpar)$}{%
      \Cparm \gets \CSetup(\secpar) \\
      (\msg_0,r_0,\msg_1,r_1) \gets \adv(\Cparm) \\
      \Ccom_0 \gets \CCommit(\Cparm,\msg_0,r_0) \\
      \Ccom_1 \gets \CCommit(\Cparm,\msg_1,r_1) \\
      \pcif \msg_0 \neq \msg_1 \land \Ccom_0 = \Ccom_1: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpComHideb(\secpar)$}{%
      \Cparm \gets \CSetup(\secpar) \\
      (\msg_0,\msg_1,st) \gets \adv(\Cparm) \\
      r \getr \mathcal{R} \\
      \Ccom \gets \CCommit(\Cparm,\msg_b,r) \\
      b' \gets \adv(st,\Ccom) \\
      \pcreturn b'
    }
  \end{minipage}
  \label{fig:com-games}
  \caption{Games for commitment schemes.}
\end{figure}

@@

\todo{Formal models on signatures over blocks of committed messages? I'm just
  informally stating a model here, but there must be some more formal
  reference...}

@@

\begin{description}
\item[$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$.] It produces public parameters
  for the other algorithms, given an input security parameter \Ssecpar.
\item[$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.] Generates a
  verification-signing key pair.
\item[$\SBCMsig \gets \langle \SBCMCom(\overline{\smsg},\smsg),
  \SBCMSign(\SBCMsk,\smsg) \rangle$.] An interactive protocol between two
  parties with shared input a block of messages \smsg. The party running
  \SBCMCom further knows a set of messages $\overline{\smsg}$ to be
  block-committed and then signed along with \smsg. The party running \SBCMSign
  controls the signing key \SBCMsk. As a result, both parties get signature
  \SBCMSig.
\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\smsg)$.] Checks whether \SBCMsig
  is a valid signature over the set of messages \smsg (independently on whether
  the messages where signed as commitments or not), under verification key
  \SBCMvk.
\end{description}

@@

Informally, an \SBCM scheme is correct if signatures generated between an honest
party running \SBCMCom with message sets $\overline{\smsg}$ and \smsg, and an
honest signer running \SBCMSign over \smsg, for honestly generated parameters
and key pairs, results in a signature over $\smsg \cup \overline{\smsg} $that is
accepted by \SBCMVerify.

A digital signature scheme is correct if honestly generated signatures, using
honestly generated key pairs, are always accepted by \SVerify. \todo{define more
  formally?}
%
A digital signature scheme \S has existential unforgeability if, for all p.p.t.
adversaries $\adv$, $\Pr[\ExpEUF = 1]$ is a negligible function of the
security parameter.

\begin{figure}[ht!]
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpSBCMEUF(\Ssecpar)$}{%
      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
      (\SBCMsig,\smsg) \gets
      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
      \pcif \SVerify(\SBCMvk,\SBCMsig,\smsg) = 0: \pcreturn 0 \\
      \pcif \nexists (\smsg',\sCcom=\CCommit(\Cparm,\smsg''))~\st~
      (\lbrace \smgs' \rbrace \cup \lbrace \smgs'' \rbrace) \subseteq \smsg
      \textrm{a query}~()~\textrm{was made to \SBCMSign}: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:euf-game}
  \caption{Existential Unforgeability Game.}
\end{figure}

@@

\paragraph{Completeness.} %
Ensures that, for any $(\NIZKx,\NIZKw) \in \NIZKRel$, any honest prover will be
able to create a proof \NIZKproof that is accepted by any honest verifier, with
overwhelming probability. More precisely, $\Pr\lbrack\ExpNIZKComp\rbrack = 1$
with overwhelming probability, for any p.p.t. \adv, for \ExpNIZKComp in
\figref{fig:nizk-games}.

\paragraph{Soundness.} %
Ensures that no adversary can create proofs accepted by \Verify, for
statements $\NIZKx \notin \NIZKLang$, except with negligible probability. That
is, for \ExpNIZKSound as in \figref{fig:nizk-games}, $\Pr\lbrack\ExpNIZKSound\rbrack
= 1$ with overwhelming probability. If this holds only against p.p.t.
adversaries, we talk of Non-Interactive \emph{arguments}, while if soundness
holds even against unbounded adversaries, we talks about Non-Interactive proofs.

\paragraph{Zero-knowledge.} %
Intuitively, captures that no information can be learned from a statement and
proof pair, beyond their validity (or not). This is captured by requiring the
adversary to distinguish between a run in the real world ($b=0$), where the
setup is done with \Setup, and $\adv$ has access to an honest prover
\Prove; and a run in an ideal world ($b=1$), where the setup is replaced by
\SimSetup, and proofs are simulated with the help of the trapdoor produced by
\SimSetup, except when $\adv$ specifies $(\NIZKx,\NIZKw) \notin \NIZKRel$. Note
that, in the context of simulation-extractable NIZK, this property not only
requires that the simulated proofs are indistinguishable to the real ones; it
also requires that \SimSetup is indistinguishable from \Setup. All this is
formalised by requiring that $|\Pr[\ExpNIZKZKb(\secpar) = 1 | b = 1] -
\Pr[\ExpNIZKZKb(\secpar) = 1 | b = 0]$ be a negligible function of \secpar,
where \ExpNIZKZKb is as defined in \figref{fig:nizk-games}.

\paragraph{Simulation-Extractability.} As stated, simulation-extractability
is an extension to simulation soundness. In a nutshell,
simulation-extractability requires that, even after having received a polynomial
number of simulated proofs of knowledge, no adversary can output a valid proof
of knowledge from which no witness can be extracted. It implies simulation
soundness, which ``just'' requires that no adversary can produce a valid proof
after having seen polynomially many simulated proofs (but does not guarantee
extraction). Formally, for simulation-extractability we require that
$\Pr[\ExpNIZKSimExt] = 1$ is a negligible function of \secpar, where
\ExpNIZKSimExt is defined in \figref{fig:nizk-games}.

\begin{figure}[ht!]
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpNIZKComp(\secpar)$}{%
      \NIZKcrs \gets \Setup(\secpar) \\
      (\NIZKx,\NIZKw) \gets \adv(\NIZKcrs) \\
      \pcif (\NIZKx,\NIZKw) \notin \NIZKRel: \pcreturn 0 \\
      \NIZKproof \gets \Prove(\NIZKcrs,\NIZKx,\NIZKw) \\
      b \gets \Verify(\NIZKcrs,\NIZKproof,\NIZKx) \\
      \pcreturn b \\
    }
    \procedure{$\ExpNIZKSimExt(\secpar)$}{%
      (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\secpar) \\
      (\NIZKx,\NIZKproof) \gets \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}
      (\NIZKcrs) \\
      \pcind \textrm{Where}~\Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
      \pcind \pcind
      \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw) \in \NIZKRel \\
      \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel \\
      \NIZKw' \gets \Extract(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKproof) \\
      \pcif \Verify(\NIZKcrs,\NIZKproof,\NIZKx) = 1 \land
      (\NIZKx,\NIZKw') \notin \NIZKRel~\land \\
      \pcind \NIZKx~\textrm{was not queried to $\Sim$ via $\Sim'$}: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }    
  \end{minipage}
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpNIZKSound(\secpar)$}{%
      \NIZKcrs \gets \Setup(\secpar) \\
      (\NIZKproof,\NIZKx) \gets \adv(\NIZKcrs) \\
      \pcif \NIZKx \notin \NIZKLang \land
      \Verify(\NIZKcrs,\NIZKproof,\NIZKx): \\
      \pcind \pcreturn 0 \\
      \pcreturn 1 \\
    }

    \procedure{$\ExpNIZKZKb(\secpar)$}{%
      \pcif b = 0: \\
      \pcind \NIZKcrs \gets \Setup(\secpar) \\
      \pcind \pcreturn \adv^{\Prove(\NIZKcrs,\cdot,\cdot)}(\NIZKcrs) \\
      \pcif b = 1: \\
      \pcind (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\secpar) \\
      \pcind \pcreturn \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}(\NIZKcrs),~
      \textrm{where} \\
      \pcind \Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
      \pcind \pcind \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw)
      \in \NIZKRel \\
      \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel
    }    
  \end{minipage}
  \label{fig:nizk-games}
  \caption{Games for Simulation-Extractable NIZK schemes.}
\end{figure}

>>>>

A digital signature scheme is correct if honestly generated signatures, using
honestly generated key pairs, are always accepted by \SVerify. 
%
A digital signature scheme \S has existential unforgeability if, for all p.p.t.
adversaries $\adv$, $\Pr[\ExpEUF(\Ssecpar) = 1]$ is a negligible function of the
security parameter.

\begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \centering
    \procedure{$\ExpEUF(\Ssecpar)$}{%
      \Sparm \gets \SSetup(\Ssecpar) \\
      (\Svk,\Ssk) \gets \SKeyGen(\Sparm) \\
      (\Ssig,\msg) \gets \adv^{\SSign(\Ssk,\cdot)}(\Svk) \\
      \pcif \SVerify(\Svk,\Ssig,\msg) = 0: \pcreturn 0 \\
      \pcif \msg~\textrm{was not queried to \SSign}: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:euf-game}
  \caption{Existential Unforgeability Game.}
\end{figure}

@@

A public-key encryption scheme is defined by the following algorithms:

\begin{description}
\item[$\Eparm \gets \ESetup(\Esecpar)$.] Produces public parameters \Eparm given
  a security parameter \Esecpar.
\item[$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$.] Given public parameters \Eparm,
  produces an encryption-decryption keypair $(\Eek,\Edk)$.
\item[$\Ec \gets \EEnc(\Eek,\msg)$.] Encrypts message \msg with encryption key
  \Eek, producing ciphertext \Ec.
\item[$\msg \gets \EDec(\Edk,\Ec)$.] Decrypts ciphertext \Ec with decryption key
  \Edk.
\end{description}

A public-key encryption scheme is correct if, given a honestly generated key
pair $(\Eek,\Edk)$, produced with honestly generated parameters \Eparm,
$\Pr[\EDec(\Edk,\EEnc(\Eek,\msg))=\msg] = 1$ with overwhelming probability.

A public-key encryption scheme has IND-CCA2 security if
$\Pr[\ExpINDCCAiio(\Esecpar) = 1] - \Pr[\ExpINDCCAiiz(\Esecpar) = 1]|$ is
a negligible function of \Esecpar, for any p.p.t. adversary \adv, where
\ExpINDCCAiib is as defined in \figref{fig:indcca2-game}.

\begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \centering      
    \procedure{$\ExpINDCCAiib(\Esecpar)$}{%
      \Eparm \gets \ESetup(\Esecpar) \\
      (\Eek,\Edk) \gets \EKeyGen(\Eparm) \\
      b^* \gets \adv^{\ELR(b,\cdot,\cdot),\EDEC(\Edk,\cdot)}(\Eek),
      ~\textrm{where:} \\
      \pcind \ELR(b,\msg_0,\msg_1)~\textrm{returns}~\EEnc(\Eek,\msg_b),
      ~\textrm{and} \\
      \pcind \EDEC(\Edk,\Ec)~\textrm{returns}~\EDec(\Edk,\Ec) \\
      \pcif \EDEC~\textrm{has been called with an output of \ELR, abort} \\
      \pcreturn b^*
    }
  \end{minipage}
  \label{fig:indcca2-game}
  \caption{IND-CCA2 Game.}
\end{figure}

@@

\begin{description}
\item[Binding.] Intuitively, the binding property of commitment schemes means
  that no adversary can change the message that has been committed to. More
  formally, $\Pr[\ExpComBind(\Csecpar) = 1]$ must be a negligible function of
  the security parameter.
\item[Hiding.] The hiding property captures that no adversary should be able to
  learn the message that was committed, when given only the commitment. This is
  formally defined through \ExpComHideb, where $|\Pr[\ExpComHideb(\Csecpar)=1|
  b=1] - \Pr[\ExpComHideb(\Csecpar)=1|b=0]|$ must be a negligible function of
  the security parameter.
\end{description}

\begin{figure}[ht!]
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpComBind(\Csecpar)$}{%
      \Cparm \gets \CSetup(\Csecpar) \\
      (\msg_0,r_0,\msg_1,r_1) \gets \adv(\Cparm) \\
      \Ccom_0 \gets \CCommit(\Cparm,\msg_0,r_0) \\
      \Ccom_1 \gets \CCommit(\Cparm,\msg_1,r_1) \\
      \pcif \msg_0 \neq \msg_1 \land \Ccom_0 = \Ccom_1: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpComHideb(\secpar)$}{%
      \Cparm \gets \CSetup(\secpar) \\
      (\msg_0,\msg_1,st) \gets \adv(\Cparm) \\
      r \getr \mathcal{R} \\
      \Ccom \gets \CCommit(\Cparm,\msg_b,r) \\
      b' \gets \adv(st,\Ccom) \\
      \pcreturn b'
    }
  \end{minipage}
  \label{fig:com-games}
  \caption{Games for commitment schemes.}
\end{figure}

@@

\todo{Formal models on signatures over blocks of committed messages? I'm just
  informally stating a model here, but there must be some more formal
  reference... \cite{cl02,asm06,ps16} all kind of allow signatures on blocks of
  (committed) messages, but they seem to use ad hoc models.}

@@

\begin{description}
\item[$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$.] It produces public parameters
  for the other algorithms, given an input security parameter \Ssecpar.
\item[$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.] Generates a
  verification-signing key pair.
\item[$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},\smsg),
  \SBCMSign(\SBCMsk,\smsg) \rangle$.] An interactive protocol between two
  parties with shared input a block of messages \smsg. The party running
  \SBCMCom further knows a set of messages $\overline{\smsg}$ to be
  block-committed and then signed along with \smsg. The party running \SBCMSign
  controls the signing key \SBCMsk. As a result, both parties get signature
  \SBCMsig over $\smsg \cup \overline{\smsg}$.
\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\smsg)$.] Checks whether \SBCMsig
  is a valid signature over the set of messages \smsg (independently on whether
  the messages where signed as commitments or not), under verification key
  \SBCMvk.
\end{description}

@@

\paragraph{Correctness.} %
Informally, an \SBCM scheme is correct if signatures generated between an honest
party running \SBCMCom with message sets $\overline{\smsg}$ and \smsg, and an
honest signer running \SBCMSign over \smsg, for honestly generated parameters
and key pairs, results in a signature over $\smsg \cup \overline{\smsg}$ that is
accepted by \SBCMVerify.

\paragraph{Unforgeability.} %
It must be unfeasible for an adversary to produce signatures over blocks of
messages that have not been signed (in plain, or committed shape) by the
signer. More formally, an \SBCM scheme is unforgeable if, for all p.p.t.
adversaries $\adv$, $\Pr[\ExpSBCMOMF(\SBCMsecpar) = 1]$, as defined in
\figref{fig:sbcm-games}, is a negligible function of the security parameter.
Note that this follows the ``one-more-forgery'' type of definition of blind
signatures \cite{bold02}.

\paragraph{Blindness.} %
Finally, the signer must not learn the plaintext values of the messages that are
signed in committed form. Note that this is a weaker notion than the usual
blindness property of blind signature schemes, where it is required that the
adversary cannot link a signature to the signing process that produced it.
Formally, blindness for \SBCM schemes is defined as in \ExpSBCMBlindb in
\figref{fig:sbcm-games}. An \SBCM scheme is blind if, for all p.p.t.
adversaries $\adv$, $|\Pr[\ExpSBCMBlindo(\SBCMsecpar) = 1] -
\Pr[\ExpSBCMBlindz(\SBCMsecpar) = 1]|$ is a negligible function of the security
parameter.

\begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \centering

    \procedure{$\ExpSBCMOMF(\SBCMsecpar)$}{%
      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
      ((\sig_1,\smsg_1),\dots,(\sig_{n+1},\smsg_{n+1})) \gets
      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
      \pcif \exists i \in [n+1]~\st~\SBCMVerify(\SBCMvk,\sig_i,\smsg_i) = 0:
      \pcreturn 0 \\
      \pcif \exists i \neq j \in [n+1]~\st~\smsg_i = \smsg_j: \pcreturn 0 \\
      \pcif \langle \cdot, \SBCMSign(\SBCMsk,\cdot)\rangle~
      \textrm{was called more than $k$ times}: \pcreturn 0 \\
      \pcreturn 1 \\
    }

    \procedure{$\ExpSBCMBlindb(\SBCMsecpar)$}{%
      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
      (\overline{\smsg}_0,\overline{\smsg}_1,\smsg) \gets
      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
      \csig \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg}_b,\smsg),
      \SBCMSign(\SBCMsk,\smsg) \rangle \\
      b^* \gets \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk,
      \csig) \\
      \pcif b = b^*: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:sbcm-games}
  \caption{Games for \SBCM schemes.}
\end{figure}

\todo{BBS+ is proven to have EUF, but nothing is said against OMF. Relationship?}

@@

\paragraph{Completeness.} %
Ensures that, for any $(\NIZKx,\NIZKw) \in \NIZKRel$, any honest prover will be
able to create a proof \NIZKproof that is accepted by any honest verifier, with
overwhelming probability. More precisely, $\Pr\lbrack\ExpNIZKComp(\NIZKsecpar)
\rbrack = 1$ with overwhelming probability, for any p.p.t. \adv, for
\ExpNIZKComp in \figref{fig:nizk-games}.

\paragraph{Soundness.} %
Ensures that no adversary can create proofs accepted by \Verify, for
statements $\NIZKx \notin \NIZKLang$, except with negligible probability. That
is, for \ExpNIZKSound as in \figref{fig:nizk-games}, $\Pr\lbrack\ExpNIZKSound
(\NIZKsecpar)\rbrack=1$ with overwhelming probability. If this holds only
against p.p.t. adversaries, we talk of Non-Interactive \emph{arguments}, while
if soundness holds even against unbounded adversaries, we talks about
Non-Interactive proofs.

\paragraph{Zero-knowledge.} %
Intuitively, captures that no information can be learned from a statement and
proof pair, beyond their validity (or not). This is captured by requiring the
adversary to distinguish between a run in the real world ($b=0$), where the
setup is done with \Setup, and $\adv$ has access to an honest prover
\Prove; and a run in an ideal world ($b=1$), where the setup is replaced by
\SimSetup, and proofs are simulated with the help of the trapdoor produced by
\SimSetup, except when $\adv$ specifies $(\NIZKx,\NIZKw) \notin \NIZKRel$. Note
that, in the context of simulation-extractable NIZK, this property not only
requires that the simulated proofs are indistinguishable to the real ones; it
also requires that \SimSetup is indistinguishable from \Setup. All this is
formalised by requiring that $|\Pr[\ExpNIZKZKb(\NIZKsecpar) = 1 | b = 1] -
\Pr[\ExpNIZKZKb(\NIZKsecpar) = 1 | b = 0]$ be a negligible function of \secpar,
where \ExpNIZKZKb is as defined in \figref{fig:nizk-games}.

\paragraph{Simulation-Extractability.} As stated, simulation-extractability
is an extension to simulation soundness. In a nutshell,
simulation-extractability requires that, even after having received a polynomial
number of simulated proofs of knowledge, no adversary can output a valid proof
of knowledge from which no witness can be extracted. It implies simulation
soundness, which ``just'' requires that no adversary can produce a valid proof
after having seen polynomially many simulated proofs (but does not guarantee
extraction). Formally, for simulation-extractability we require that
$\Pr[\ExpNIZKSimExt(\NIZKsecpar)] = 1$ is a negligible function of \secpar,
where \ExpNIZKSimExt is defined in \figref{fig:nizk-games}.

\begin{figure}[ht!]
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpNIZKComp(\NIZKsecpar)$}{%
      \NIZKcrs \gets \Setup(\NIZKsecpar) \\
      (\NIZKx,\NIZKw) \gets \adv(\NIZKcrs) \\
      \pcif (\NIZKx,\NIZKw) \notin \NIZKRel: \pcreturn 0 \\
      \NIZKproof \gets \Prove(\NIZKcrs,\NIZKx,\NIZKw) \\
      b \gets \Verify(\NIZKcrs,\NIZKproof,\NIZKx) \\
      \pcreturn b \\
    }
    \procedure{$\ExpNIZKSimExt(\NIZKsecpar)$}{%
      (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\NIZKsecpar) \\
      (\NIZKx,\NIZKproof) \gets \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}
      (\NIZKcrs) \\
      \pcind \textrm{Where}~\Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
      \pcind \pcind
      \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw) \in \NIZKRel \\
      \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel \\
      \NIZKw' \gets \Extract(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKproof) \\
      \pcif \Verify(\NIZKcrs,\NIZKproof,\NIZKx) = 1 \land
      (\NIZKx,\NIZKw') \notin \NIZKRel~\land \\
      \pcind \NIZKx~\textrm{was not queried to $\Sim$ via $\Sim'$}: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }    
  \end{minipage}
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpNIZKSound(\NIZKsecpar)$}{%
      \NIZKcrs \gets \Setup(\NIZKsecpar) \\
      (\NIZKproof,\NIZKx) \gets \adv(\NIZKcrs) \\
      \pcif \NIZKx \notin \NIZKLang \land
      \Verify(\NIZKcrs,\NIZKproof,\NIZKx): \\
      \pcind \pcreturn 0 \\
      \pcreturn 1 \\
    }

    \procedure{$\ExpNIZKZKb(\NIZKsecpar)$}{%
      \pcif b = 0: \\
      \pcind \NIZKcrs \gets \Setup(\NIZKsecpar) \\
      \pcind \pcreturn \adv^{\Prove(\NIZKcrs,\cdot,\cdot)}(\NIZKcrs) \\
      \pcif b = 1: \\
      \pcind (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\secpar) \\
      \pcind \pcreturn \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}(\NIZKcrs),~
      \textrm{where} \\
      \pcind \Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
      \pcind \pcind \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw)
      \in \NIZKRel \\
      \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel
    }    
  \end{minipage}
  \label{fig:nizk-games}
  \caption{Games for Simulation-Extractable NIZK schemes.}
\end{figure}
